{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-06-23 Mobility_Pattern_Twitter_Landuse/main.tex
xx
hurry up

\documentclass[fleqn,10pt]{wlscirep}
\title{Scientific Reports Title to see here (20 words or less)}

@@

\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

@@

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Figueredo:2009dg}.

\section*{Acknowledgements (not compulsory)}

@@

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\title{Understanding Human Mobility Patterns from Semantic Twitter User Trajectories}

@@

\begin{abstract}
xx
\end{abstract}
\begin{document}
\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}
The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

The discovery and identifications of Lévy flight distribution, however, the implication of Lévy flight is that the process illustrates randomness.

@@

\section*{Methods}
Contextualizing the semantic meaning of the geo-located tweets

Spatial entropy

Spatial dispersion

Mobility shape

First passage time model

\bibliography{ref}

\section*{Acknowledgements}

@@

Must include all authors, identified by initials, for example:
J.Y. conceived the experiment(s),  J.Y. conducted the experiment(s), J.Y. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}
The authors declare no competing financial interests.
\end{document}

### 2016-06-23 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
hurry up

%\begin{figure}[ht]
%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
%\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
%\label{S1_Fig}
%\end{figure}

@@

\subsection{Geo-located Twitter Data}
A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
For this study, geo-located tweets were collected using the Twitter Streaming API (
{\tt{https://dev.twitter.com/streaming/overview}}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest. To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively. This does include the whole of Ireland part of France.
We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
The collected point visualization reveals the geography of cities.
Notice the clusters with higher densities of tweets correspond to the locations of major cities.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\linewidth]{./figure/uk}
\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to a geo-located tweet collected for this study. Twitter activity is most apparent in urban areas.}
\label{S2_Fig}
\end{center}
\end{figure}

To verify the collected tweets are from human users, the raw tweets were further filtered using the following steps.
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
We adopted a relocation speed threshold of 240 m/s as used by \citep{jurdak2015}. 
We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.

@@

To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\citep{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\citep{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings. 
To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \citep{gonzalez2008,jurdak2015}.
The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:

@@

>>>>

@@

\subsection{Geo-located Twitter Data and Data Processing}
A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
For this study, geo-located tweets were collected using the Twitter Streaming API (
{\tt{https://dev.twitter.com/streaming/overview}}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest. To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively. This does include the whole of Ireland part of France.
We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
The collected point visualization reveals the geography of cities.
Notice the clusters with higher densities of tweets correspond to the locations of major cities.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\linewidth]{./figure/S2_twitter_density_Fig_1}
\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study. Twitter activity is most apparent in urban areas.}
\label{S2_Fig}
\end{center}
\end{figure}

To remove tweets of non-human users from the collected database, the raw tweets were further filtered using the following steps.
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.

@@

To build the spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\citep{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\citep{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings. 
To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \citep{gonzalez2008,jurdak2015}.
The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:

@@

\begin{equation} \label{eq:3}
<T_{ij}>=k*\dfrac{P_{i} * P_{j}}{f(d_{ij})},  \textrm{and}\hspace{1ex} f(d_{ij}) \sim d_{ij}^{\beta}
\end{equation}
